Coherent optical association of single molecules

### 2020-09-16 paper.tex
Format/whitespace

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $50 \%$ \todo{number}.
  The molecule has a (change to 8.8G) zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
  and lifetime up to $1 \mathrm{ms}$ \todo{number}. (center of mass motional state population.)
  %We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
  This  technique is general (does not rely on narrow excited state linewidth) and could allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

%the requirement of a suitable FB resonance limits its generality. \todo{e.g. non-magnetic atoms?}

%The size mismatch between the initial and final states cause a very small coupling between them,
%which poses the biggest challege for for coherent creation of the molecule.

@@

%In this letter, we will present our result on coherent creation of a weakly bond molecule
%using only optical transitions on a broad optical line for the first time.

%The optical transfer scheme we use is shown in figure \todo{}. To drive the atoms from
% We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state. In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state. \todo{move selection of intermediate state to intro?}. For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency. Therefore, in our experiment, we selected the v=0 state as the intermediate state for our Raman transition.

@@

%In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.

@@

%The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

@@

We locate the Raman resonance for the atom to molecule transition at $770... MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288... GHz$ which corresponds to a $... GHz$ single photon detuning. (We can maybe add information about the prediction here?)
The background level of $...\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy (can this be considered "interaction shift spectroscopy"?). When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
We observed the narrowest linewidth of $.... kHz$ for the Raman resonance at a pulse time of $... ms$, which corresponds to a linewidth-pulsetime product of $...$. This is consistent with the expected value of $...$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent. In order to verify the coherence of the transfer directly, we fixed the Raman frequency on the resonance and scanned the pulse time. figure ... shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transfered into the molecular state.

@@

%% Prediction

%This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288... GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770... MHz$. \todo{more, mention/cite Jeremy}

>>>>

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $50 \%$ \todo{number}.
  The molecule has a (change to 8.8G) zero-field binding energy of $770 \mathrm{MHz}$ \todo{number}
  and lifetime up to $1 \mathrm{ms}$ \todo{number}. (center of mass motional state population.)
  % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
  This  technique is general (does not rely on narrow excited state linewidth) and could allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

% the requirement of a suitable FB resonance limits its generality. \todo{e.g. non-magnetic atoms?}

% The size mismatch between the initial and final states cause a very small coupling between them,
% which poses the biggest challege for for coherent creation of the molecule.

@@

% In this letter, we will present our result on coherent creation of a weakly bond molecule
% using only optical transitions on a broad optical line for the first time.

% The optical transfer scheme we use is shown in figure \todo{}. To drive the atoms from
% We use an optical Raman transition to drive the system from the atomic initial state to a ground electronic molecular state. In order to reduce the size mismatch between the atomic and molecular states, we selected the first bound state for the 3322 spin state \todo{asymtopt to the 3322 threshold?} as our final state. \todo{move selection of intermediate state to intro?}. For similar reason, the natural choice for the intermediate excited molecular state is one with highly excited motional level.However, from our calculation (and experiment?), the smaller level space for high vibrational state and the smaller detuning from the atomic threshold increases the scattering rate of the molecular state which causes a reduced Raman Rabi frequency to decoherence rate ratio and a lower transfer efficiency. Therefore, in our experiment, we selected the v=0 state as the intermediate state for our Raman transition.

@@

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.

@@

% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

@@

We locate the Raman resonance for the atom to molecule transition at $770... MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288... GHz$ which corresponds to a $... GHz$ single photon detuning. (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288... GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770... MHz$. \todo{more, mention/cite Jeremy}
The background level of $...\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy (can this be considered "interaction shift spectroscopy"?). When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
We observed the narrowest linewidth of $.... kHz$ for the Raman resonance at a pulse time of $... ms$, which corresponds to a linewidth-pulsetime product of $...$. This is consistent with the expected value of $...$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent. In order to verify the coherence of the transfer directly, we fixed the Raman frequency on the resonance and scanned the pulse time. figure ... shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transfered into the molecular state.

@@
